Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-05-18 prop_letter.tex
prop_letter.tex Fix some typos...

First for each interval $[\ell,r]$ we have the natural constraint
$0 \leq \ell \leq r \leq 1$ that guarantees that every element of the
interval can be interpreted as a conventional probability. We also
include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals to
refer to the probability of impossible events (e.g., the null event)
and certain events (e.g., the event covering the entire sample space
). For each interval $[\ell,r]$, we also need the interval
$[1-r,1-\ell]$ so that if one interval refers to the probability of an
event, the other refers to the probability of the complement
event. For example, if we discover as a result of an experiment that
$\mu(E) = [0.2,0.3]$ for some event~$E$, we may conclude thatv
$\mu(\overline{E}) = [0.7,0.8]$ for the complement event
$\overline{E}$. In addition to these simple conditions, there are some
subtle conditions on how intervals are combined, which we discuss
next.

@@

The expectation value is intuitively between two possible outcomes
which lie between the minimum and maximum bounds of the given
probability intervals, and this definition also consistent with the classical
Choquet integral on commuting sub-event space by adopting the classical
theorem~\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.
If the QIVPM is crypto-deterministic, this
interval collapses to a singleton $\left\{ \lambda\right\} $, where
$\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
and $\left\{ \lambda_{2}\right\} $ to be
$\left\{ \lambda_{1}\lambda_{2}\right\} $, then we have
\begin{equation}
\prod_{j=1}^{N}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{N}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
\end{equation}
for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.

>>>>

First for each interval $[\ell,r]$ we have the natural constraint
$0 \leq \ell \leq r \leq 1$ that guarantees that every element of the
interval can be interpreted as a conventional probability. We also
include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals to
refer to the probability of impossible events (e.g., the null event)
and certain events (e.g., the event covering the entire sample space).
For each interval $[\ell,r]$, we also need the interval
$[1-r,1-\ell]$ so that if one interval refers to the probability of an
event, the other refers to the probability of the complement
event. For example, if we discover as a result of an experiment that
$\mu(E) = [0.2,0.3]$ for some event~$E$, we may conclude that
$\mu(\overline{E}) = [0.7,0.8]$ for the complement event
$\overline{E}$. In addition to these simple conditions, there are some
subtle conditions on how intervals are combined, which we discuss
next.

@@

The expectation value is intuitively between two possible outcomes
which lie between the minimum and maximum bounds of the given
probability intervals, and this definition also consistent with the classical
Choquet integral on commuting sub-event space by adopting the classical
results~\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.
If the QIVPM is crypto-deterministic, this
interval collapses to a singleton $\left\{ \lambda\right\} $, where
$\lambda$ is an eigenvalue of $\mathbf{O}$. If we define the
multiplication of two singleton sets~$\left\{ \lambda_{1}\right\} $
and $\left\{ \lambda_{2}\right\} $ to be
$\left\{ \lambda_{1}\lambda_{2}\right\} $, then we have
\begin{equation}
\prod_{j=1}^{N}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{N}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
\end{equation}
for any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.
